Correlations between gender and research topics at three major archaeology conferences

### 2020-07-18 analysis/paper/paper.Rmd
update dicsussion

Our results show correlations between the gender of the first-named presenter and the topics in their conference presentation. Although each of the three meetings have distinctive sets of topics, we can identify some common themes in the topics that correlate with

>>>>

Our results show significant correlations between the gender of the first-named presenter and the topics in their conference presentation in all three conferences. Although each of the three meetings have distinctive sets of topics, we can identify some common themes in the topics that correlate with gender.
